# Full Genome, Random Social Learning

So far all simulations with the full genome are done with a cost for y and z = 1

```{r,eval=TRUE}
load(file="data/fullgenomeRandom.bin")
moving_thetaRandom=moving_theta
moving_thetaRandom$distX=abs(moving_thetaRandom$theta - moving_thetaRandom$mean_x)
load(file="data/fullgenome.bin")
moving_thetaBest=moving_theta
moving_thetaBest$distX=abs(moving_thetaBest$theta - moving_thetaBest$mean_x)
```

```{r}
uniquesetupRandomMULT=moving_thetaRandom[ moving_thetaRandom$sigma == 1 & moving_thetaRandom$delta == 1 & moving_thetaRandom$m == .5 & moving_thetaRandom$vt == .001 & moving_thetaRandom$K == 2000 & moving_thetaRandom$mu == 0.01 & moving_thetaRandom$omega == 4,]
uniquesetupRandomMuLT=moving_thetaRandom[ moving_thetaRandom$sigma == 1 & moving_thetaRandom$delta == 1 & moving_thetaRandom$m == .5 & moving_thetaRandom$vt == .001 & moving_thetaRandom$K == 2000 & moving_thetaRandom$mu == 0.001 & moving_thetaRandom$omega == 4,]
uniquesetupBestMULT=moving_thetaBest[ moving_thetaBest$sigma == 1 & moving_thetaBest$delta == 1 & moving_thetaBest$m == .5 & moving_thetaBest$vt == .001 & moving_thetaBest$K == 2000 & moving_thetaBest$mu == 0.01 & moving_thetaBest$omega == 4,]
uniquesetupBestMuLT=moving_thetaBest[ moving_thetaBest$sigma == 1 & moving_thetaBest$delta == 1 & moving_thetaBest$m == .5 & moving_thetaBest$vt == .001 & moving_thetaBest$K == 2000 & moving_thetaBest$mu == 0.001 & moving_thetaBest$omega == 4,]

uniquesetupRandomMUHT=moving_thetaRandom[ moving_thetaRandom$sigma == 1 & moving_thetaRandom$delta == 1 & moving_thetaRandom$m == .5 & moving_thetaRandom$vt == .02 & moving_thetaRandom$K == 2000 & moving_thetaRandom$mu == 0.01 & moving_thetaRandom$omega == 4,]
uniquesetupRandomMuHT=moving_thetaRandom[ moving_thetaRandom$sigma == 1 & moving_thetaRandom$delta == 1 & moving_thetaRandom$m == .5 & moving_thetaRandom$vt == .02 & moving_thetaRandom$K == 2000 & moving_thetaRandom$mu == 0.001 & moving_thetaRandom$omega == 4,]
uniquesetupBestMUHT=moving_thetaBest[ moving_thetaBest$sigma == 1 & moving_thetaBest$delta == 1 & moving_thetaBest$m == .5 & moving_thetaBest$vt == .02 & moving_thetaBest$K == 2000 & moving_thetaBest$mu == 0.01 & moving_thetaBest$omega == 4,]
uniquesetupBestMuHT=moving_thetaBest[ moving_thetaBest$sigma == 1 & moving_thetaBest$delta == 1 & moving_thetaBest$m == .5 & moving_thetaBest$vt == .02 & moving_thetaBest$K == 2000 & moving_thetaBest$mu == 0.001 & moving_thetaBest$omega == 4,]
```


## Mean fitness with and distance to $\theta$

### Low rate of change  ($vt = 0.01$)
Random Social Learning (top), Best Social Learning (bottom)  high $\mu=0.01$ (left), low $\mu = 0.001$ (right)
```{r}
par(mfrow=c(2,2))
plotDistVsFitness(uniquesetupRandomMULT,main="mu=0.01, random copy")
plotDistVsFitness(uniquesetupRandomMuLT,main="mu=0.001, random copy")
plotDistVsFitness(uniquesetupBestMULT,main="mu=0.01, copy the best")
plotDistVsFitness(uniquesetupBestMuLT,main="mu=0.001, copy the best")
```

### High rate of change ($vt = 0.2$)
Random Social Learning (top), Best Social Learning (bottom)  high $\mu=0.01$ (left), low $\mu = 0.001$ (right)
```{r}
par(mfrow=c(2,2))
plotDistVsFitness(uniquesetupRandomMUHT,main="mu=0.01, random copy")
plotDistVsFitness(uniquesetupRandomMuHT,main="mu=0.001, random copy")
plotDistVsFitness(uniquesetupBestMUHT,main="mu=0.01, copy the best")
plotDistVsFitness(uniquesetupBestMuHT,main="mu=0.001,copy the best")
```

## Compare the mean value of the three genes during the simulation

### Low rate of change ($vt = 0.01$)
Random Social Learning (top), Best Social Learning (bottom)  high $\mu=0.01$ (left), low $\mu = 0.001$ (right)
```{r}
par(mfrow=c(2,2))
plot3Genes(uniquesetupRandomMULT,main="mu=0.01, random copy")
plot3Genes(uniquesetupRandomMuLT,main="mu=0.001, random copy")
plot3Genes(uniquesetupBestMULT,main="mu=0.01, copy the best")
plot3Genes(uniquesetupBestMuLT,main="mu=0.001, copy the best")
```

### High rate of change($vt = 0.2$) 
Random Social Learning (top), Best Social Learning (bottom)  high $\mu=0.01$ (left), low $\mu = 0.001$ (right)
```{r}
par(mfrow=c(2,2))
plot3Genes(uniquesetupRandomMUHT,main="mu=0.01, random copy")
plot3Genes(uniquesetupRandomMuHT,main="mu=0.001, random copy")
plot3Genes(uniquesetupBestMUHT,main="mu=0.01, copy the best")
plot3Genes(uniquesetupBestMuHT,main="mu=0.001, copy the best")
```

## Compare $\omega$, $\delta$, and rate of increase

With $\mu = 0.01$ and $m=.5$

```{r,fig.width=10,fig.height=10}
MMTR=moving_thetaRandom[ moving_thetaRandom$sigma == 1 & moving_thetaRandom$m == .5  & moving_thetaRandom$K == 2000 & moving_thetaRandom$mu == 0.01 ,]
ds=unique(MMTR$delta)
vts=unique(MMTR$vt)
colds=rev(colorRampPalette(c("red","blue"))(length(ds)))
names(colds)=ds
par(mfrow=c(3,3))
for(d in unique(MMTR$omega)){
    for(var in c("mean_z","mean_y","distX")){
        vtDelta=tapply(MMTR[,var][MMTR$omega==d],MMTR[MMTR$omega == d,c("vt","delta")],mean)
        plot(1,1,type="n",main=bquote(omega==.(d)),ylim=range(vtDelta,na.rm=T),xlim=range(vts),xlab="vt",ylab=var)
        for(i in ds)lines(vts,vtDelta[,as.character(i)],col=colds[as.character(i)],lwd=2)
    }
}
legend("topleft",legend=sapply(ds,function(d)as.expression(bquote(delta==.(d)))),lwd=2,lty=1,col=colds)
```

With $\mu = 0.001$ and $m=.2$

```{r,fig.width=10,fig.height=10}
MMTR=moving_thetaRandom[ moving_thetaRandom$sigma == 1 & moving_thetaRandom$m == .2  & moving_thetaRandom$K == 2000 & moving_thetaRandom$mu == 0.001 ,]
ds=unique(MMTR$delta)
vts=unique(MMTR$vt)
colds=colorRampPalette(c("red","blue"))(length(ds))
names(colds)=ds
par(mfrow=c(3,3))
for(d in unique(MMTR$omega)){
    for(var in c("mean_z","mean_y","distX")){
        vtDelta=tapply(MMTR[,var][MMTR$omega==d],MMTR[MMTR$omega == d,c("vt","delta")],mean)
        plot(1,1,type="n",main=bquote(omega==.(d)),ylim=range(vtDelta,na.rm=T),xlim=range(vts),xlab="vt",ylab=var)
        for(i in ds)lines(vts,vtDelta[,as.character(i)],col=colds[as.character(i)],lwd=2)
    }
}
legend("topleft",legend=sapply(ds,function(d)as.expression(bquote(delta==.(d)))),lwd=2,lty=1,col=colds)
```

   



## Different environmental variance

###  Population Size
Check the trajectory of  the effective population size with rate of changes = 0.02 and autocorrelation $\omega = 4$

#### Random Copy
```{r,fig.width=10,fig.height=10}
    plotAllTrajVar(moving_thetaRandom[moving_thetaRandom$vt == 0.02& moving_thetaBest$omega == 4,],m=0.5,E=0,obs="N")
```

#### Copy the Best
```{r,fig.width=10,fig.height=10}
    plotAllTrajVar(moving_thetaBest[moving_thetaBest$vt == 0.02& moving_thetaBest$omega == 4,],m=0.5,E=0,obs="N")
```

### Distance to Optimum
Check the trajectory of the distance to optimum:

#### Random Copy 
```{r,fig.width=10,fig.height=10}
    plotAllTrajVar(moving_thetaRandom[moving_thetaRandom$vt == 0.02& moving_thetaBest$omega == 4,],m=0.5,E=0,obs="dist")
```

#### Copy the Best
```{r,fig.width=10,fig.height=10}
    plotAllTrajVar(moving_thetaBest[moving_thetaBest$vt == 0.02& moving_thetaBest$omega == 4,],m=0.5,E=0,obs="dist")
```

###  Fitness

Check the trajectory of the distance to optimum:

#### Random Copy 
```{r,fig.width=10,fig.height=10}
    plotAllTrajVar(moving_thetaRandom[moving_thetaRandom$vt == 0.02& moving_thetaBest$omega == 4,],m=0.5,E=0,obs="mean_w")
```

#### Copy the Best
```{r,fig.width=10,fig.height=10}
    plotAllTrajVar(moving_thetaBest[moving_thetaBest$vt == 0.02& moving_thetaBest$omega == 4,],m=0.5,E=0,obs="mean_w")
```

## Value at equilibrium

```{r,fig.width=10,fig.height=10}
mtr=moving_thetaRandom[moving_thetaRandom$omega== 4 & moving_thetaRandom$vt== 0.02,]
mtb=moving_thetaBest[moving_thetaBest$omega== 4 & moving_thetaBest$vt== 0.02,]
plotAllVariableSummaries(mtr,E=0,estimate=NULL,var="distX") #we use only simulations without noise
plotAllVariableSummaries(mtr,E=0,estimate=NULL,var="mean_y") #we use only simulations without noise
plotAllVariableSummaries(mtr,E=0,estimate=NULL,var="mean_z") #we use only simulations without noise
plotAllVariableSummaries(mtb,E=0,estimate=NULL,var="distX") #we use only simulations without noise
plotAllVariableSummaries(mtb,E=0,estimate=NULL,var="mean_y") #we use only simulations without noise
plotAllVariableSummaries(mtb,E=0,estimate=NULL,var="mean_z") #we use only simulations without noise
```



## Social Learning vs rates, autocorel and variance:

plot(1,1,ylim=c(0,1))
