# LR04 stack + interpolation


## Dataset 

```{r echo=FALSE, message=FALSE}
folderexpe="exploreRealEnvRANDOMNoisyHigherRes"
idexpe="stackLR04InterpolNoisyRescale"

ns=length(list.files(path=folderexpe,recursive=T,full.names=T,pattern="*cross*"))

realdata=read.csv("data/lr04.csv")
newt=interpolate(realdata$dOsea,realdata$year,finalres=250)
epoch=min(-realdata$year):max(-realdata$year)
epoch=epoch*1000

binded=do.call("rbind",lapply(list.files(path=folderexpe,recursive=T,full.names=T,pattern="*cross*"),function(u){load(u);return(binded)}))
allEs=unique(binded$E)
allSigmas=unique(binded$sigma)

load(file=as.character(binded$filename[1]))
nsteps=nrow(summary)



binded=binded[binded$sigma==0.5,]
binded=binded[binded$E==.2,]

```

For this sexperiment we test the data from the stack LR04
Stack LR04 is made of `r nrow(realdata)` records, describing between 1000 and 2500 years, for a total of mor than 5M years, shown in Figure \@ref(fig:realdataLR04). But to icrease the resolution of this dataset we interpolate date point between the one we have.


## General properties at the end of the simulation

```{r}
t=c("NA","N","3Genes")
allsummaries=unlist(lapply(allSigmas,function(s)paste0('images/',idexpe,t,'_sigma',s,'_E.png')))
```

```{r outputEndNI, out.width = "30%", fig.cap="Summary output at the end of the simulation (from top to bottom $\\sigma_s = 0.5,1$)",fig.show="hold",fig.link=allsummaries}
knitr::include_graphics(as.character(allsummaries))
```


## Strategies Distribution Through Time Vertical visualisation
 
Rows in those graphs represent 500 years from -120,000 (top) to 0 (the year 2000) at the bottom. Columns represents different  parameter combination. The main order is the cost of $y$, then the cost of $z$ and the smaller level of orderare the parameter related to mutation (from left to right $\mu \times m$ increase).  Each figure shows a different $\sigma_s$.

```{r}
allimg=unlist(lapply(allSigmas[2],function(s)paste0("images/vertical_",idexpe,"_sigma",s,"_E",allEs,".png")))
```

```{r compactNoisyRandomNI, out.width = "24%", fig.cap="Compact vertical trajectories (from top to bottom $\\sigma_s = 0.5,1$, from left to right, $E=0,0.2,0.6,1$)",fig.show="hold",fig.link=allimg}
knitr::include_graphics(as.character(allimg))
```

 

```{r}
allimg=unlist(lapply(allSigmas[2],function(s)paste0("images/verticalMHghRes_",idexpe,"_sigma",s,"_E",allEs,".png")))
```
```{r individualTraj, out.width = "24%", fig.cap="Compact vertical trajectories  for individual trajectories:(from top to bottom $\\sigma_s = 0.5,1$, from left to right, $E=0,0.2,0.6,1$)",fig.show="hold",fig.link=allimg}
knitr::include_graphics(as.character(allimg))
```
