# Real Environment, Noisy Interpolation, Rescaled


## Dataset 

```{r echo=FALSE, message=FALSE}
folderexpe="exploreRealEnvRANDOMNoisyHigherResHighSigma"
idexpe="stackLR04InterpolNoisyRescale"

ns=length(list.files(path=folderexpe,recursive=T,full.names=T,pattern="*cross*"))

realdata=read.csv("data/theta_real.csv")
newt=interpolate(realdata$permille,realdata$years.BP.2000,finalres=.25)
epoch=min(-realdata$years.BP.2000):max(-realdata$years.BP.2000)
epoch=epoch*1000

binded=do.call("rbind",lapply(list.files(path=folderexpe,recursive=T,full.names=T,pattern="*cross*"),function(u){load(u);return(binded)}))
allEs=unique(binded$E)
allSigmas=unique(binded$sigma)

load(file=as.character(binded$filename[1]))
nsteps=nrow(summary)



```

For this experiment we rescale the LR04 by simply mutliply by -5. See section envrionment for more reflection on rescaling.

```{r realdataLR04rescale,echo=FALSE, message=FALSE,fig.cap="Rescaled data from Stack LR04 Lisiecki et. al 2004"}
plot(realdata$years,-5*realdata$permille,ylab="rescaled delta 18",,xlab="Age (kyear BP)",type="l")
```

## General properties at the end of the simulation

```{r outputEndNIRS, out.width = "30%", fig.cap="Summary output at the end of the simulation (from top to bottom $\\sigma_s = 1,2$)",fig.show="hold"}
t=c("NA","N","3Genes")
allsummaries=unlist(lapply(allSigmas,function(s)paste0('images/',idexpe,t,'_sigma',s,'_E.png')))
knitr::include_graphics(as.character(allsummaries))
```


## Observe Strategies Distributions full trajectories 

```{r,echo=F,fig.width=3,fig.height=3, out.width = "32%", results='asis'}

binded=binded[binded$sigma==1,]
binded=binded[binded$E==.2,]
```

In the next section we explore the proportion of different strategies with different $\mu$ and $m$, but keeping only the results for $\sigma_s=$ `r paste0(unique(binded$sigma))` and $E=$ `r paste0(unique(binded$E))` :

* $\mu$ decrease from top to bottom following those values:
$\mu=$ `r paste0(rev(unique(binded$mu))) `

* $m$ increase from left to right following those values:
$m=$ `r paste0(unique(binded$m)) `

The orange, blue and  purple hard lines represent the median of the proportion of the three strategies within the population for `r ns` repetitions. The lighter lines represents the 5 and 95% percentiles (as we may be interested in situations where social learning, or mixed strategies, emerges, though not often).

```{r,echo=F,fig.width=3,fig.height=3, out.width = "32%", results='asis'}

for(s in unique(binded$sigma)){
    for(kz in unique(binded$k_z)){
        for(ky in unique(binded$k_y)){
            cat(paste0("### $\\sigma$ = ",s,", $k_z$ = ",kz,", $k_y$ = ",ky,"\n\r"), sep="")
            for(mu in rev(unique(binded$mu))){
                for(m in unique(binded$m)){
                    subb=droplevels(binded[binded$mu ==mu &binded$m ==m &binded$sigma ==s & binded$k_z ==kz & binded$k_y ==ky,])
                    nexpe=nrow(subb)
                    vars=c("prop_y","prop_z","prop_yz","mean_x","N","mean_p")
                    names(vars)=vars
                    mat_allexp= lapply(vars,function(i)matrix(NA,nexpe,nsteps))

                    for(i in 1:nexpe){
                        load(as.character(subb$filename[i]))
                        for(v  in vars) mat_allexp[[v]][i,]=summary[,v]
                    }
                    sum_mat=lapply(mat_allexp,function(m)apply(m,2,quantile,probs=c(.05,.5,.95),na.rm=T))
                    fname=paste0("traj_s",s,"_m",m,"_mu",mu,"_ky",ky,"_kz",kz,".png")
                    plotMatrixStrateAndEn(sum_mat,rev(5*newtN),epoch)
                    mtext(bquote(sigma[s] == .(s) ~ mu == .(mu) ~ m == .(m) ),3,0,outer=T)
                }
            }
            cat(paste0("\n\r---\n\r", sep=""))
        }
    }
}

```

## Strategies Distribution Through Time Compact visualisation
 
```{r compactNoisyRandomNIRS, out.width = "24%", fig.cap="Compact vertical trajectories (from top to bottom $\\sigma_s = 1,2$, from left to right, $E=0,0.2,0.6,1$)",fig.show="hold"}
allimg=unlist(lapply(allSigmas,function(s)paste0("images/vertical_",idexpe,"_sigma",s,"_E",allEs,".png")))
knitr::include_graphics(as.character(allimg))
```
