# Results  Simulations Multiple Environments

In this section we run simulations with the different environments presented in the section \@ref(real-env) after applying the different subsampling methods or different way to interpolate missing data points.

For each environment we run a set of simulation exploring different parameters. Each unique combination of parameter is run 20 times. For each combination of simulations we report mean population size, the number of extenctions and the mean genotype. We also reproduce the full trajectories as vertical colored band representing the 1/ mean genotype for the 20 simulations 2/ each simulation as a single vertical band.

All data are used after being rescaled following Vostok temperature estimates.
The resample/interpolation function used are

1. `Noisy Interpolation`: generating missing datapoints be using the random noise generator using parameter calculate from NGRIP dataset.
2. `getClosest`: evenly resampling and taking the closest data points

Final resolution: every 20years, 



```{r}
    #namesRealEnv=c("epica","lr04","ls16","vostok","ngrip","martrat","ngrip2")
    namesRealEnv=c("vostok","ngrip2","martrat","ngrip","ls16")
    namesFun=c("interpolate_Sls")
    namesSLS=c("random","fitprop")
    suf="NEWF"
    allEs=1
    allSigmas=3:5

```

```{r}

basecaption1=paste0('(from top to bottom $\\\\sigma_s =',paste0(allSigmas, collapse = ","),'$, real E: $E_x=0.1,E_y=1,E_z=.5$, SLS:{{sls}} Environment:{{env}})')
basecaption2=paste0('(from top to right $\\\\sigma_s =',paste0(allSigmas, collapse = ","),'$, real E: $E_x=0.1,E_y=1,E_z=.5$, SLS:{{sls}} Environment:{{env}})')
a=c(
    "### {{sls}}",
    '```{r}',
    'idexpe="{{id}}"',
    #'t=c("NA","N","3Genes")',
    #'allsummaries=unlist(lapply(allSigmas,function(s)paste0("images/",idexpe,t,"_sigma",s,"_E.png")))',
    'allimg=unlist(lapply(allSigmas,function(s)paste0("images/vertical_",idexpe,"_sigma",s,"_E1.png")))',
    '```',
    #"#### Last step summary",
    #paste0('```{r summary-last-{{id}}, out.width = "33%", fig.cap="Summary output for last step',basecaption1,'",fig.show="hold",fig.link=allsummaries}'),
    #'knitr::include_graphics(as.character(allsummaries))',
    #'```',
    "#### Vertical summary",
    paste0('```{r traj-{{id}}, out.width = "33%", fig.cap="Summarized vertical trajectories',basecaption2,'",fig.show="hold",fig.link=allimg}'),
    'knitr::include_graphics(as.character(allimg))',
    '```',
    '```{r}',
    'allimg=unlist(lapply(allSigmas,function(s)paste0("images/verticalMz_",idexpe,"_sigma",s,"_E",allEs,".png")))',
    '```',
    "#### Vertical run indiv",
    paste0('```{r traj-ind-{{id}}, out.width = "33%", fig.cap="Vertical trajectories for 20 individual runs',basecaption2,'",fig.show="hold",fig.link=allimg}'),
    'idexpe="{{id}}"',
    'knitr::include_graphics(as.character(allimg))',
    '```',
    '```{r}',
    'allimg=unlist(lapply(allSigmas,function(s)paste0("images/vertical_N_Mz_",idexpe,"_sigma",s,"_E",allEs,".png")))',
    '```',
    "#### Vertical run indiv: $N_e$",
    paste0('```{r traj-indN-{{id}}, out.width = "33%", fig.cap="Vertical trajectories for 20 individual runs, $N_e$',basecaption2,'",fig.show="hold",fig.link=allimg}'),
    'idexpe="{{id}}"',
    'knitr::include_graphics(as.character(allimg))',
    '```'
    )

```

```{r,include=FALSE,echo=T}
src <- lapply(namesRealEnv,function(env)c(knitr::knit_expand(text="## {{env}} ",env=env),lapply(namesSLS,function(sls)knitr::knit_expand(text=a,id=paste0(env,namesFun,sls,suf),env=env,sls=sls))))

```

`r knitr::knit_child(text=unlist(src))`


