# Exploring Sigmas X,Y, and Z Genes


```{r,eval=FALSE}
moving_theta=getAlllSummaries("testSigmas")
moving_theta=updateScale(moving_theta)
moving_theta$distX=abs(moving_theta$theta-moving_theta$mean_x)
save(file="data/moving_thetaXYZ.bin",moving_theta)
```

```{r}
load(file="data/moving_thetaXYZ.bin")
```


## Compare final mean value of x,y and given $\sigma_s$ and $\sigma_y$, Low rate of change ($vt=0.002$), $\omega = 2$ and $m=.2$ and $2\times\sigma_y = \sigma_z$

```{r,fig.width=7,fig.height=7}
par(mfrow=c(2,3))
for(m in unique(moving_theta$mu)){
    for(var in c("distX","mean_y","mean_z")){
        uniquesetup=moving_theta[ moving_theta$m == .2 &  moving_theta$vt == .002 & moving_theta$omega == 2 & moving_theta$K == 2000 & moving_theta$mu == m & moving_theta$k_z==2& moving_theta$delta==.5,]
        sigmas=sort(unique(uniquesetup$sigma))
        ks=sort(unique(uniquesetup$k_y))
        colsigmas=colorRampPalette(c("red","blue"))(length(sigmas))
        names(colsigmas)=sigmas
        sigmaK = tapply( uniquesetup[,var],uniquesetup[,c("sigma","k_y")],mean,na.rm=T)
        plot(1,1,type="n",main=bquote(mu==.(m)),ylim=range(sigmaK,na.rm=T),xlab="k_y",ylab=var,xlim=range(ks))
        for(i in sigmas)lines(ks,sigmaK[as.character(i),],col=colsigmas[as.character(i)],lwd=2,type="b")
        legend("topleft",legend=sapply(sigmas,function(d)as.expression(bquote(sigma[s]==.(d)))),lwd=2,lty=1,col=colsigmas)
    }
}
```

## Compare final mean value of x,y and given $\sigma_s$ and $\sigma_y$, $vt=0.002$ , $\omega = 2$ and $m=.2$ and $8\times\sigma_y = \sigma_z$

```{r,fig.width=7,fig.height=7}
par(mfrow=c(2,3))
for(m in unique(moving_theta$mu)){
    for(var in c("distX","mean_y","mean_z")){
        uniquesetup=moving_theta[ moving_theta$m == .2 &  moving_theta$vt == .002 & moving_theta$omega == 2 & moving_theta$K == 2000 & moving_theta$mu == m & moving_theta$k_z==8 & moving_theta$delta==.5,]
        sigmas=sort(unique(uniquesetup$sigma))
        ks=sort(unique(uniquesetup$k_y))
        colsigmas=colorRampPalette(c("red","blue"))(length(sigmas))
        names(colsigmas)=sigmas
        sigmaK = tapply( uniquesetup[,var],uniquesetup[,c("sigma","k_y")],mean,na.rm=T)
        plot(1,1,type="n",main=bquote(mu==.(m)),ylim=range(sigmaK,na.rm=T),xlab="k_y",ylab=var,xlim=range(ks))
        for(i in sigmas)lines(ks,sigmaK[as.character(i),],col=colsigmas[as.character(i)],lwd=2,type="b")
        legend("topleft",legend=sapply(sigmas,function(d)as.expression(bquote(sigma[s]==.(d)))),lwd=2,lty=1,col=colsigmas)
    }
}
```

## Compare final mean value of x,y and given $\sigma_s$, $\sigma_y$,$\sigma_z$ $vt=0.2$ , $\omega = 2$ and $m=.2$ and $2\times\sigma_y = \sigma_z$

### Low $\delta=.5$

```{r,fig.width=7,fig.height=7}
par(mfrow=c(2,3))
for(m in unique(moving_theta$mu)){
    for(var in c("distX","mean_y","mean_z")){
        uniquesetup=moving_theta[ moving_theta$m == .2 &  moving_theta$vt == .2 & moving_theta$omega == 2 & moving_theta$K == 2000 & moving_theta$mu == m & moving_theta$k_z==2 & moving_theta$delta == .5,]
        sigmas=sort(unique(uniquesetup$sigma))
        ks=sort(unique(uniquesetup$k_y))
        colsigmas=colorRampPalette(c("red","blue"))(length(sigmas))
        names(colsigmas)=sigmas
        sigmaK = tapply( uniquesetup[,var],uniquesetup[,c("sigma","k_y")],mean,na.rm=T)
        plot(1,1,type="n",main=bquote(mu==.(m)),ylim=range(sigmaK,na.rm=T),xlab="k_y",ylab=var,xlim=range(ks))
        for(i in sigmas)lines(ks,sigmaK[as.character(i),],col=colsigmas[as.character(i)],lwd=2,type="b")
        legend("topleft",legend=sapply(sigmas,function(d)as.expression(bquote(sigma[s]==.(d)))),lwd=2,lty=1,col=colsigmas)
    }
}
```

## Compare final mean value of x,y and given $\sigma_s$ and $\sigma_y$, $vt=0.2$ , $\omega = 2$ and $m=.2$ and $8\times\sigma_y = \sigma_z$

### Low $\delta=.5$

```{r,fig.width=7,fig.height=7}
par(mfrow=c(2,3))
for(m in unique(moving_theta$mu)){
    for(var in c("distX","mean_y","mean_z")){
        uniquesetup=moving_theta[ moving_theta$m == .2 &  moving_theta$vt == .2 & moving_theta$omega == 2 & moving_theta$K == 2000 & moving_theta$mu == m & moving_theta$k_z==8 & moving_theta$delta == .5,]
        sigmas=sort(unique(uniquesetup$sigma))
        ks=sort(unique(uniquesetup$k_y))
        colsigmas=colorRampPalette(c("red","blue"))(length(sigmas))
        names(colsigmas)=sigmas
        sigmaK = tapply( uniquesetup[,var],uniquesetup[,c("sigma","k_y")],mean,na.rm=T)
        plot(1,1,type="n",main=bquote(mu==.(m)),ylim=range(sigmaK,na.rm=T),xlab="k_y",ylab=var,xlim=range(ks))
        for(i in sigmas)lines(ks,sigmaK[as.character(i),],col=colsigmas[as.character(i)],lwd=2,type="b")
        legend("topleft",legend=sapply(sigmas,function(d)as.expression(bquote(sigma[s]==.(d)))),lwd=2,lty=1,col=colsigmas)
    }
}
```





## Plot trajectories of the three genes:
### Low rate of change (vt = 0.002) and $\sigma_z = 2\times\sigma_y$
Parameter: m = .2 , vt = .002, omega= 2, K = 2000 delta=.5
```{r,fig.width=10,fig.height=5}
par(mfrow=c(1,3))
for(m in unique(moving_theta$mu)){
    #for(var in c("distX","mean_y","mean_z")){
        uniquesetup=moving_theta[ moving_theta$m == .2 &  moving_theta$vt == .002 & moving_theta$omega == 2 & moving_theta$K == 2000 & moving_theta$mu == m & moving_theta$k_z==2 & moving_theta$delta == .5,]
        sigmas=sort(unique(uniquesetup$sigma))
        ks=sort(unique(uniquesetup$k_y))
        for(i in sigmas){
            for(j in ks){
                plot3Genes(uniquesetup[uniquesetup$sigma==i & uniquesetup$k_y==j,],side="topleft",main=bquote( mu == .(m) ~ k[z] == 2 ~ k[y]== .(j) ~ sigma[s] == .(i)))
            }
        }
    #}
}
```

### High rate of change (vt = 0.2) and $\sigma_z = 2\times\sigma_y$
Parameter: m = .2 , vt = .2, omega= 2, K = 2000 , delta=.5
```{r,fig.width=10,fig.height=5}
par(mfrow=c(1,3))
for(m in unique(moving_theta$mu)){
    #for(var in c("distX","mean_y","mean_z")){
        uniquesetup=moving_theta[ moving_theta$m == .2 &  moving_theta$vt == .2 & moving_theta$omega == 2 & moving_theta$K == 2000 & moving_theta$mu == m & moving_theta$k_z==2 & moving_theta$delta == 2,]
        sigmas=sort(unique(uniquesetup$sigma))
        ks=sort(unique(uniquesetup$k_y))
        for(i in sigmas){
            for(j in ks){
                plot3Genes(uniquesetup[uniquesetup$sigma==i & uniquesetup$k_y==j,],side="topleft",main=bquote( mu == .(m) ~ k[z] == 2 ~ k[y]== .(j) ~ sigma[s] == .(i)))
            }
        }
    #}
}
```


## Plot trajectories of the three genes:
### Low rate of change (vt = 0.002) and $\sigma_z = 2\times\sigma_y$
Parameter: m = .2 , vt = .002, omega= 2, K = 2000 delta=.5
```{r,fig.width=10,fig.height=5}
par(mfrow=c(1,3))
for(m in unique(moving_theta$mu)){
    #for(var in c("distX","mean_y","mean_z")){
        uniquesetup=moving_theta[ moving_theta$m == .2 &  moving_theta$vt == .002 & moving_theta$omega == 2 & moving_theta$K == 2000 & moving_theta$mu == m & moving_theta$k_z==2 & moving_theta$delta == 2,]
        sigmas=sort(unique(uniquesetup$sigma))
        ks=sort(unique(uniquesetup$k_y))
        for(i in sigmas){
            for(j in ks){
                plot3Genes(uniquesetup[uniquesetup$sigma==i & uniquesetup$k_y==j,],side="topleft",main=bquote( mu == .(m) ~ k[z] == 2 ~ k[y]== .(j) ~ sigma[s] == .(i)))
            }
        }
    #}
}
```

### High rate of change (vt = 0.2) and $\sigma_z = 2\times\sigma_y$
Parameter: m = .2 , vt = .2, omega= 2, K = 2000 , delta=.5
```{r,fig.width=10,fig.height=5}
par(mfrow=c(1,3))
for(m in unique(moving_theta$mu)){
    #for(var in c("distX","mean_y","mean_z")){
        uniquesetup=moving_theta[ moving_theta$m == .2 &  moving_theta$vt == .2 & moving_theta$omega == 2 & moving_theta$K == 2000 & moving_theta$mu == m & moving_theta$k_z==2 & moving_theta$delta == .5,]
        sigmas=sort(unique(uniquesetup$sigma))
        ks=sort(unique(uniquesetup$k_y))
        for(i in sigmas){
            for(j in ks){
                plot3Genes(uniquesetup[uniquesetup$sigma==i & uniquesetup$k_y==j,],side="topleft",main=bquote( mu == .(m) ~ k[z] == 2 ~ k[y]== .(j) ~ sigma[s] == .(i)))
            }
        }
    #}
}
```



